Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-05-19 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] updates concerning B->K* form factor treatments

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain parameters
  of their $q^2$-dependence,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
  \todo{update $B\to K^*$ form factors}
}
\end{center}
\end{table*}

@@

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the
imaginary parts of vectorial couplings.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B\to K^*\bar\mu\mu$ integrated over
     $q^2$ bins at low- and high-$q^2$ for several new physics scenarios respecting
     all the considered experimental constraints. The SM prediction with respective
     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

@@

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline
  \multicolumn{4}{c}{$B\to K^*$ form factors}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

@@

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccc}
        \hline
        $q^2$ [\GeV$^2$] & $17$            & $20$            & $23$\\
        \hline
        $f_0(q^2)$   & $0.62 \pm 0.03$ & $0.72 \pm 0.03$ & $0.87 \pm 0.04$\\
        $f_+(q^2)$   & $1.13 \pm 0.05$ & $1.63 \pm 0.07$ & $2.68 \pm 0.13$\\
        $f_T(q^2)$   & $1.02 \pm 0.06$ & $1.47 \pm 0.08$ & $2.42 \pm 0.18$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV$^2$]
             & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
        \hline
   $f_0(17)$ & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010 & 0.048 \\
   $f_0(20)$ & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093 & 0.075 \\
   $f_0(23)$ & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046 & 0.058 \\
   $f_+(17)$ & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21  & 0.051 \\
   $f_+(20)$ & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26  & 0.20  \\
   $f_+(23)$ & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14  & 0.22  \\
   $f_T(17)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79  & 0.46  \\
   $f_T(20)$ & --    & --   & --   & --   & --   & --   & --    & 1.00  & 0.85  \\
   $f_T(23)$ & --    & --   & --   & --   & --   & --   & --    & --    & 1.00  \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        $B\to K$ form factors $f_{0,+,T}(q^2)$.
        \label{tab:btok-lattice}
      }
\end{table}

We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
(SSE) \cite{Bharucha:2010im}
\begin{align}
  \label{eq:SSE-FF-parameterization}
  F_i(q^2) & =
  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
\end{align}
with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}$
and two ($k=1,2$) for $i= A_{12}$. The parameters $\alpha_0^i$ correspond to
$F_i(q^2 = 0)$ and the kinematic constraint
\begin{align}
  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,,
\end{align}
is used to eliminate $\alpha_0^{A_{12}}$, where the kinematic factor
${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
given in \cite{Straub:2015ica}.

This parameterization allows us to combine consistently available results
of form factors from different non-perturbative approaches, namely LCSR's at
large recoil and lattice at low recoil and implement simultaneously additional
kinematic constraints. We determine the parameters $\alpha_i^k$
in a combined fit to form factor predictions of $V, A_{0,1,12}$ from the LCSR
\cite{Straub:2015ica} and lattice \cite{Horgan:2013hoa, Horgan:2015vla} calculations,
including their correlations. Further, we implement the second kinematic constraint
\begin{align}
  \label{eq:A12-constraint-q2max}
  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
\end{align}
at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
are chosen for all $\alpha_k^i$
\begin{align}
  \alpha_0^i & \in [0,\, 1] \,, &
  \alpha_{1,2}^i & \in [-10,\, 10].
\end{align}
The results of the LCSR predictions of the form factors have been provided to us
directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12}$, including their $16\times16$
correlation matrix. In the case of lattice predictions, we proceed as in our
previous work \cite{Beaujean:2013soa} by generating form factor values of
$V,\, A_{0,1,12}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
see \reftab{tab:btokstar-lattice}.

We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
versus two parameters only and found that in the latter case lattice form factor
results influence the fit such that form factors tend to be higher than LCSR
predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
setup as it accommodates better LCSR and lattice results.

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|cc}
        \hline
        $q^2$ [\GeV$^2$] & $15$            & $19.21$ \\
        \hline
        $V(q^2)$         & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
        $A_0(q^2)$       & $0.62 \pm 0.03$ & $0.72 \pm 0.03$\\
        $A_1(q^2)$       & $1.13 \pm 0.05$ & $1.63 \pm 0.07$\\
        $A_{12}(q^2)$    & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV$^2$]
                & $15$  & $19$ & $15$ & $19$ & $15$ & $19$ & $15$  & $19$ \\
        \hline
   $V(15)$      & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010\\
   $V(19)$      & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093\\
   $A_0(15)$    & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046\\
   $A_0(19)$    & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21 \\
   $A_1(15)$    & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26 \\
   $A_1(19)$    & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14 \\
   $A_{12}(15)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79 \\
   $A_{12}(19)$ & --    & --   & --   & --   & --   & --   & --    & 1.00 \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Horgan:2015vla} for the
        $B\to K^*$ form factors $V(q^2)$ and $A_{0,1,12}(q^2)$.
        \todo{Enter correct numbers from constraint.cc}
        \label{tab:btokstar-lattice}
      }
\end{table}

>>>>

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensorial coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available. }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio and the rate CP asymmetry
of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the
imaginary parts of vectorial couplings.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
  & 1
  &
  & SM
  &
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$ 
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prediction with respective
     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

@@

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline \hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline \hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline \hline
  \multicolumn{4}{c}{$B\to K^*$ form factors}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

@@

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccc}
        \hline
        $q^2$ [\GeV$^2$] & $17$            & $20$            & $23$\\
        \hline
        $f_0(q^2)$   & $0.62 \pm 0.03$ & $0.72 \pm 0.03$ & $0.87 \pm 0.04$\\
        $f_+(q^2)$   & $1.13 \pm 0.05$ & $1.63 \pm 0.07$ & $2.68 \pm 0.13$\\
        $f_T(q^2)$   & $1.02 \pm 0.06$ & $1.47 \pm 0.08$ & $2.42 \pm 0.18$\\
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV$^2$]
             & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
        \hline
   $f_0(17)$ & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010 & 0.048 \\
   $f_0(20)$ & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093 & 0.075 \\
   $f_0(23)$ & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046 & 0.058 \\
   $f_+(17)$ & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21  & 0.051 \\
   $f_+(20)$ & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26  & 0.20  \\
   $f_+(23)$ & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14  & 0.22  \\
   $f_T(17)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79  & 0.46  \\
   $f_T(20)$ & --    & --   & --   & --   & --   & --   & --    & 1.00  & 0.85  \\
   $f_T(23)$ & --    & --   & --   & --   & --   & --   & --    & --    & 1.00  \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        $B\to K$ form factors $f_{0,+,T}(q^2)$.
        \label{tab:btok-lattice}
      }
\end{table}

We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
(SSE) \cite{Bharucha:2010im}
\begin{align}
  \label{eq:SSE-FF-parameterization}
  F_i(q^2) & =
  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
\end{align}
with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}, 
T_{1,23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
correspond to $F_i(q^2 = 0)$ and the kinematic constraints
\begin{align}
  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,, &
  T_1(0) & = T_2(0)
\end{align}
are used to eliminate $\alpha_0^{A_{12}, T_2}$, where the kinematic factor
${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
given in \cite{Straub:2015ica}.

This parameterization allows us to combine consistently available results
of form factors from different non-perturbative approaches, namely LCSR's at
large recoil and lattice at low recoil and implement simultaneously the
kinematic constraints. We determine the parameters $\alpha_i^k$
in a combined fit to form factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the
LCSR \cite{Straub:2015ica} and of $V, A_{0,1,12},T_{1,2,23}$ from the lattice
\cite{Horgan:2013hoa, Horgan:2015vla} calculations,
including their correlations. Further, we implement the second kinematic constraint
\begin{align}
  \label{eq:A12-constraint-q2max}
  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
\end{align}
at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
are chosen for all $\alpha_k^i$
\begin{align}
  \alpha_0^i & \in [0,\, 1] \,, &
  \alpha_{1}^i & \in [-2,\, 2]  \,, &
  \alpha_{2}^i & \in [-3,\, 3] \,.
\end{align}
The results of the LCSR predictions of the form factors have been provided to us
directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12},\, T_{1,2,3}$, including their $28\times 28$
covariance matrix. \todo{In the case of lattice predictions, we proceed as in our
previous work \cite{Beaujean:2013soa} by generating form factor values of
$V,\, A_{0,1,12},\, T_{1,2,3}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
see \reftab{tab:btokstar-lattice}.}

\todo{We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
versus two parameters only and found that in the latter case lattice form factor
results influence the fit such that form factors tend to be higher than LCSR
predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
setup as it accommodates better LCSR and lattice results.}
